%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
<<<<<<< ba3bf043d0c6d5a43d3bf7f2e7c2932c59fa1edf
\cvsection{Experiences}
=======
\vspace{2pt}
\cvsection{Pracovní zkušenosti}
>>>>>>> added stuff to add as text


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
<<<<<<< ba3bf043d0c6d5a43d3bf7f2e7c2932c59fa1edf
    {SW Developer Internship}
    {Tieto Czech Support Services s.r.o.}
    {Brno}
    {July 2016 - Present}
    {
      \begin{cvitems}
       \item {Getting to know OpenStack - virtualization technology and OpenDaylight - software defined networking.}
       \item {Working on integration between these two along with OpenvSwitch and DPDK.}
       \item {Exploring features (mininet - Python, Virtual Tenant Network - REST \dots) of OpenDaylight and making automatization scripts using bash.}
      \end{cvitems}
    }
  \cventry
    {NOC operator} % Job title
    {GiTy, a.s.} % Organization
    {Brno} % Location
    {April 2014 - June 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
	\item {Technical supervision of MPLS network, satellite network (VSAT) iDirect and Hughes.}
        \item {Contact with a customer and managing of unexpected incidents on the network, potential change in configuration of the network on Mikrotik/Cisco devices.}     
        \item {Network behaviour analysis, including modelling with tool SNMPc and using network monitoring program PRTG.}     
        \item {Processing of customer's demands in system helpdesk or creating SLA reports using vba macros.}        
      \end{cvitems}
    }
   \cventry
   {IT Technician}
   {Zabezpečovací systémy a sítě Studený}
   {Říčany u Brna}
   {November 2013}
   {
    \begin{cvitems}
      \item {Building up LAN infrastructure, adding a network rack.}
    \end{cvitems}
   }
   \cventry
   {IT Technician}
   {Komply.cz}
   {Brno}
   {May 2013}
   {
    \begin{cvitems}
      \item {Building up LAN infrastructure; computer configuration, maintanance.}
    \end{cvitems}
   }
   \cventry
   {Practical training}
   {GiTy, a.s.}
   {Brno}
   {March 2013 - May 2013}
   {
    \begin{cvitems}
      \item {Getting familiar with company's data services, terrestrial and satellite services. Work on a supervision center and it's technical support.}
      \item {Work related to G-Net network node modernization. Switching of the data lines or expansion of the network devices by adding additional modules and their configuration.}
    \end{cvitems}
   }
   
   \cventry
   {Practical training}
   {ABA Czech, s.r.o.}
   {Hustopeče}
   {2010}
   {
    \begin{cvitems}
      \item {Getting to know system Novell, reinstallation of computers with OS Microsoft Windows.}
    \end{cvitems}
   }
=======
    {Pomocná projektantka} % Job title
    {Moravia Wood Trading s.r.o.} % Organization
    {Šenov} % Location
    {Duben 2015 - Červen 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Tvorba návrhu architektonické studie RD.}
        \item {Zpracování projektové dokumentace na PC (MS Office, ArchiCAD).}
        %\item {Inženýrská činnost (zajištění stanovisek dotčených orgánů státní správy, správců sítí). \newline Tvorba návrhu architektonické studie a interiéru RD.}
      \end{cvitems}
    }
   \cventry
   {Práce na farmě}
   {Peter Marshall \& Co.}
   {Alyth, UK}
   {Červenec - Srpen (2011, 2012, ...2015)}
   {
    \begin{cvitems}
      \item {Sběr ovoce}
    \end{cvitems}
   }
   \cventry
   {Prodavačka obuvi a doplňků}
   {Destroy}
   {Praha}
   {Červenec - Srpen (2007, 2008, 2009)}
   {
    \begin{cvitems}
      \item {Aktivní prodej produktů a služeb zákazníkům na prodejně.}
    \end{cvitems}
   }
  
>>>>>>> added stuff to add as text

%---------------------------------------------------------
\end{cventries}
